Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-02-12 paper_jasa.tex
question for Di/Heike

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.7}{\includegraphics{power_loess_exp3.pdf}}
       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of UMP test for sample size $n= 100$ and $\sigma = 5$ as per experiment 3.}
       \label{fig:power_loess3}
\end{figure*}

@@

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{power_observed_exp3.pdf}}
       \caption{Observed power of visual test from equation \eqref{power_est} with pointwise 95\% confidence limits and the power of UMP test for sample size $n= 100$ and $\sigma = 5$ as per experiment 3.}
       \label{fig:power_observed_exp3}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_percent_correct.pdf}}
       \caption{Percentage of correct responses decreases rapidly with the increase of p-value. After p-value exceed 1.5 it is very unlikely to identify the observed plot. The theoretical justification of this is shown in figure \ref{fig:pval_power}}
       \label{fig:pval_pcorrect}
\end{figure*}

>>>>

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.4}{\includegraphics{power_loess_exp3.pdf}}
       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of UMP test for sample size $n= 100$ and $\sigma = 5$ as per experiment 3. Notice that for experiment 3, power does not seem to depend on the parameter $\beta$. Di/Heike, I am not sure how I can relate this to demonstrate the power of visual inference when normal conditions are not met. Does this really test our hypothesis $H_0: \beta=0$ or some other hypothesis about the existence of cluster in the data?}
       \label{fig:power_loess3}
\end{figure*}

@@

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{power_observed_exp3.pdf}}
       \caption{Observed power of visual test from equation \eqref{power_est} with pointwise 95\% confidence limits and the power of UMP test for sample size $n= 100$ and $\sigma = 5$ as per experiment 3. }
       \label{fig:power_observed_exp3}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_percent_correct.pdf}}
       \caption{Percentage of correct responses decreases rapidly with the increase of p-value. After p-value exceeds 1.5 it is very unlikely to identify the observed plot. The theoretical justification of this is shown in figure \ref{fig:pval_power}}
       \label{fig:pval_pcorrect}
\end{figure*}
